Fusion Moves for Correlation Clustering

### 2014-10-29 paper/egpaper_for_review.tex
worked on text

\todo[inline]{should there be a general introduction to multicuts?}

Given an edge weighted graph, positive weights (\emph{attractive})
encourage the adjacent nodes to be in the same 
connected component, while negative weights (\emph{repulsive}) encourage
the nodes to stay in different connect components.
Therefore the sign of the weights encodes if two
nodes should be merged or not and the magnitude of the weights encodes
the certainty of this desire.
The objective of correlation clustering / multicuts
is finding the cut with a minimal sum of cut edge weights.
The number of connected components / clusters is discovered
from the weights ( rewrite?!?).
Correlation clustering / the multicut is NP-hard \cite{???}.
%
Despite the NP-hardness, correlation clustering has been 
successfully used for
\begin{inparaenum}[(i)]
    \item partitioning a superpixel region adjacency graph~\cite{andres_2011_iccv,kroeger_2012_eccv}
    \item with optional long range repulsive edges~\cite{andres_2013_emmcvpr}.
    \item Alush and Globerger showed how to average multiple segmentations with the multicut objective~\cite{alush_2012_pami}.
    \item Multicuts can also be used for interactive segmentation~\cite{bagon_2011_arxiv},
    \item for co-segmentation~\cite{glassner_2011_cvpr}
    \item and to cluster fully connected graphs~\cite{???}.
\end{inparaenum}

\todo[inline]{WHY WE NEED THIS NEW SOLVER?}

Nunez-Iglesias \etal describe the multicut as
\say{one-shot agglomeration of supervoxels} whose 
main drawback is the scalability \cite{nunez_iglesias_2013}.

\todo[inline]{BETTER MOTIVATE SUPERNODES}

To address scalability, supernodes can be useful.
To create supernodes, some edges will be contracted
and their nodes are merged into super-nodes.
Doing so, we can reduce  the graph 
to a reasonable size, such that we can find
global optimal multicut solutions within reasonable time.
%
Any edge which is contracted is lost.
If such an edge is cut in the global optimal solution, we cannot 
find this global optimal solutions.
Therefore we avoid fixed decisions and use a
dynamic energy aware contraction scheme.
%
Different edge contractions lead to different super-node graphs.
A trivial approach is the following.
Create different super-node graphs, optimize them with multicuts,
and take the result which leads to the lowest energy
on the unmodified initial graph.
% 
Doing so, we throw away all results which do not have the lowest energy.
Within this work we propose a framework which 
combine multiple \emph{proposal} super-node graphs
without any premature irreversible decisions.
Furthermore, multiple super-node graphs are combined such
that the information form all of them is used.
\todo[inline]{\emph{proposal} super-node graphs sounds shitty}
%
The proposed algorithm can be interpreted as a fusion moves
algorithm for correlation clustering / multicut objective.
We generate cheap and versatile proposals
and \emph{fuse} them with the current best solution with the
guarantee that this cannot increase the energy.

\textbf{Contribution:}

\textbf{Outline:}

%-------------------------------------------------------------------------

\section{Problem Formulation}
Def: Graph, weighted graph, cut, multicut

@@

\section{Related Work}

% \subsubsection{Solver for the Multicut Objective}

    \input{inputs/tab_mc_overview.tex}

\subsection{Correlation Clustering}
   \begin{itemize}
   \item Multicut~\cite{kappes_2011_emmcvpr}
   \item Expand and Explorer~\cite{bagon_2011_arxiv}
   \item Fast Planar CC~\cite{yarkony_2012_eccv}
   \item Break and Conquer \cite{alush_2013_simbad}.
   \item Cut Glue And Cut~\cite{beier_2014_cvpr}
   \end{itemize}

\subsection{Fusion Moves}
Move making algorithms, in particular fusion moves, 
have become increasingly popular for energy minimization~\cite{???,kappes_2014_ws}.
For many large scale computer vision applications fusion moves lead to good approximations
with state of the art any time performance~\cite{kappes_2014_ws}.

@@

%------------------------------------------------------------------------
\section{Correlation-Clustering-Fusion (CCF) Moves}
Motivation Using Fusion moves -> problem ambiguity

@@

\section{Experiments}

@@

\section{Further Work}
So far we have generated the proposals randomly and do not take the current segmentation into account.

@@

\section{Conclusion}

>>>>

Given an edge weighted graph, positive weights (\emph{attractive})
encourage the adjacent nodes to be in the same 
connected component, while negative weights (\emph{repulsive}) encourage
the nodes to stay in different connect components.
Therefore the sign of the weights encodes if two
nodes should be merged or not and the magnitude of the weights encodes
the certainty of this desire.
The objective of correlation clustering / multicuts
is finding the cut with a minimal sum of cut edge weights.
The number of connected components / clusters is discovered
from the weights ( rewrite?!?).
Correlation clustering / the multicut is NP-hard \cite{???}.
%
Despite the NP-hardness, correlation clustering has been 
successfully used for
\begin{inparaenum}[(i)]
    \item partitioning a superpixel region adjacency graph~\cite{andres_2011_iccv,kroeger_2012_eccv}
    \item with optional long range repulsive edges~\cite{andres_2013_emmcvpr}.
    \item Alush and Globerger showed how to average multiple segmentations with the multicut objective~\cite{alush_2012_pami}.
    \item Multicuts can also be used for interactive segmentation~\cite{bagon_2011_arxiv},
    \item for co-segmentation~\cite{glassner_2011_cvpr}
    \item and to cluster sparse and graphs~\cite{???}.
\end{inparaenum}

Despite the nice properties of correlation clustering
to perform a \say{one-shot agglomeration of supervoxels} ~\cite{nunez_iglesias_2013},
the main draw back of correlation clustering is scalability~\cite{nunez_iglesias_2013}.
Existing solvers for correlation clustering do not scale for non planar graphs.
Even state of the art approximate move making algorithm fail 
to give good approximations non planar graphs.
When increasing the problem sizes, either the runtime explodes or the 
approximations are far away from being useful.

\textbf{Contribution:}
\begin{inparaenum}[(i)]
\item Within this work we propose a fast and scalable move making algorithm for correlation clustering,
\item which generalized  fusion moves \cite{???} to correlation clustering problems.
\item We reduce the inference to a series of moves where
each moves optimizes over a subspace spanned by the current best solution
and a proposal solution.
\item We propose two versatile proposal generators,
\item and show how to optimize these moves.
\item We give a polyhedral interpretation of this algorithm,
\item and evaluate the proposed method 
on existing benchmark problems.
\item We show state of the art any time performance on those instances.
\end{inparaenum}[(i)]

\textbf{Outline:}
In sec.~\ref{sec:problem_formulation} we will give a 
detailed problem definition where we introduce 
the correlation clustering objective.
In sec.~\ref{sec:related_work} we will 
discuss existing methods for correlation 
clustering and briefly explain the concept of fusion moves.
In sec: ~\ref{sec:cc_fm} we describe our proposed
method and show the properties of the algorithm.
In sec.~\ref{sec:exp} we show an evaluation
of the method on existing parameter  and discuss the effects of parameters.
Future work will be discussed in sec. \ref{sec:future} and
we will conclude in ~\ref{sec:conclusion}.
%-------------------------------------------------------------------------

\section{Problem Formulation}\label{sec:problem_formulation}
Def: Graph, weighted graph, cut, multicut

@@

\section{Related Work}\label{sec:related_work}

\subsection{Correlation Clustering}\label{sec:cc}
A major branch of research has focused on solving 
relaxations of eq.~\ref{eq:edgeproblem} by linear programming
or solving  eq.~\ref{eq:edgeproblem} directly to global optimality
by using integer linear programming in a cutting plane fashion  \cite{kappes_2011_emmcvpr,andres_2011_iccv}.

Yarkony et al ~\cite{yarkony_2012_eccv} uses 
a dual decomposition based approach for planar graphs
where the subproblems are planar max cut instances.

An other branch of research uses move making algorithm 
to optimize correlation clustering.
Bansal and Bagon use a modified $\alpha-$expansion \cite{bansal_2004_ml} 
algorithm suitable for correlation clustering,
while the state of the art method from  Beier \etal~\cite{beier_2014_cvpr} iteratively re-optimizes the cuts
between adjacent connected components.

   % \begin{itemize}
   % \item Multicut~\cite{kappes_2011_emmcvpr}
   % \item Expand and Explorer~\cite{bagon_2011_arxiv}
   % \item Fast Planar CC~\cite{yarkony_2012_eccv}
   % \item Break and Conquer \cite{alush_2013_simbad}.
   % \item Cut Glue And Cut~\cite{beier_2014_cvpr}
   % \end{itemize}

\subsection{Fusion Moves}\label{sec:fm}
Move making algorithms, in particular fusion moves, 
have become increasingly popular for energy minimization~\cite{???,kappes_2014_ws}.
For many large scale computer vision applications fusion moves lead to good approximations
with state of the art any time performance~\cite{kappes_2014_ws}.
The fusion move algorithm works as follows:
A current best solution is maintained and proposal solutions 
are generated.
Within each move, the variables can choose the label from the current best or from the 
proposed solution. This problem can be formulated as an 
optimization problem with a binary label space.
Any optimal solution of this auxiliary problem is guaranteed
to not worsen the current best solution.

@@

%------------------------------------------------------------------------
\section{Correlation-Clustering-Fusion (CCF) Moves}\label{sec:cc_fm}
Motivation Using Fusion moves -> problem ambiguity

@@

\section{Experiments}\label{sec:exp}

@@

\section{Further Work}\label{sec:future}
So far we have generated the proposals randomly and do not take the current segmentation into account.

@@

\section{Conclusion}\label{sec:conclusion}
